---
title: "First Assignment"
author: "Marcio Woitek"
date: "8/17/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Solution

### Tasks 1 and 2

I begin by creating a couple of lists, as instructed. Here is a bulleted list
with a sub-list:

* First item.
* An item with a sub-list:
  + Item a.
  + Item b.
* Last item.

I have just finished task 1. Next, I will create a numbered list.

1. Grocery shopping
2. Email mom
3. Get lunch
4. Go on walk

The second task is now complete.

### Tasks 3 and 4

For the third task, I have to include some *italicized words*. And, for task 4,
I need to add some **words in bold print**. This should convince you that I
know how to **bold** and *italicize* text.

### Task 5

I've already used different headers. But, in case you still need to be
convinced that I know how to create them, I'll include a few more:

#### Header

##### Another header
\
\
I believe this is enough.

### Task 6

I will write some code that adds two numbers. You should be able to see the
corresponding output. But my code will be hidden.

```{r hidden-code, echo=FALSE}
num_1 <- 10L
num_2 <- 20L
my_sum <- num_1 + num_2
sprintf("%d + %d = %d", num_1, num_2, my_sum)
```

### Task 7

As instructed, next I will create a table. Specifically, I will generate a
table that contains important Unix commands.

| Name | Category           | Description                   |
|------|--------------------|-------------------------------|
| cd   | Filesystem         | Change the working directory  |
| kill | Process management | Terminate or signal processes |
| sed  | Text processing    | Stream editor                 |

### Task 8

For task 8, I will plot the following quadratic function:

$$y = f(x) = x^2 - 4x$$

To generate this plot, I will use the `curve` function.

```{r plot-quadratic-function}
curve(
  x^2 - 4 * x,
  from = -1,
  to = 5,
  xlab = "x",
  ylab = "y"
)
```

### Task 9

The next step is to print my session info. The command for doing so is below.
The output of this command is a little different from what you would expect.
The reason is that I ran this code on my personal computer.

```{r print-session-info, R.options = list(width = 80)}
sessionInfo()
```

### Tasks 10 and 11

Recall that the last two tasks are the following:

* Execute .Rmd file.
* Upload knitted PDF.

Obviously, these are problems that I cannot solve **here**. However, if you are
reading this document, this is a pretty good indication that I succeeded.
